---
title: Table output
output: 
  html_document: default
  pdf_document: default
---

### LaTeX

* A `pdf` document uses [LaTeX](https://www.latex-project.org/) under the hood to compile a `.tex` file to `pdf`.

* In latex a table is written as (see source Rmd file)


\begin{center}
\begin{tabular}{rr}
\hline
Var1 & Var2 \\
\hline
1 & 2 \\
3 & 4\\
\hline
\end{tabular}
\end{center}

### Markdown 

* A markdown table is written as (see source Rmd file)

| Var1| Var2|
|----:|----:|
|    1|    2|
|    3|    4|


* A table can be created by using `knitr`'s `kable` function as below:


### Using `kable` function 

We'll learn more about code chunks next.

```{r challenge-01}
df <- data.frame(Var1 = c(1, 3),
                 Var2 = c(2, 4))
knitr::kable(df)
```

### HTML 

This is a html table:

<table>
 <thead>
  <tr>
   <th style="text-align:right;"> Var1 </th>
   <th style="text-align:right;"> Var2 </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 2 </td>
  </tr>
  <tr>
   <td style="text-align:right;"> 3 </td>
   <td style="text-align:right;"> 4 </td>
  </tr>
</tbody>
</table>


# Output specific evaluation

```{r, eval=knitr::is_latex_output(), echo = FALSE, results = "asis"}
stargazer::stargazer(df, header = FALSE)
```
