---
title: 'ETC5523: Communicating with Data'
subtitle: "Tutorial 3 Supp B"
author: "Emi Tanaka"
date: "Week 3"
output: pdf_document
---

```{r setup, include = FALSE}
library(palmerpenguins)
library(tidyverse)
library(stargazer)
library(MASS)
knitr::opts_chunk$set(
  echo = FALSE
)
```


```{r, results='asis'}
penguins %>% 
  select_if(is.numeric) %>% 
  as.data.frame() %>% # stargazer doesn't work with tibbles!!
  stargazer(header = FALSE, 
            covariate.labels = c("Bill length (mm)", "Bill depth (mm)", "Flipper length (mm)", "Body mass (g)", "Year"),
            title = "Summary statistics")
```

```{r, include = FALSE}
lm1 <- step(lm(bill_length_mm ~ ., data = penguins))
rlm1 <- rlm(bill_length_mm ~ ., data = penguins)
```


```{r, eval = FALSE}
# easier to manually add the factor column
stargazer(lm1, rlm1, header = FALSE, 
          title = "Regression results",
          dep.var.labels = "Bill length (mm)",
          covariate.labels = c("Chinstrap", "Genotoo", "Dream", "Torgersen", "Bill depth (mm)", "Flipper length (mm)", "Body mass (g)", "Male", "Year", "Constant")
          )
```

\begin{table}[!htbp] \centering 
  \caption{Regression results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}llcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
&  & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
\cline{3-4} 
\\[-1.8ex] & & \multicolumn{2}{c}{Bill length (mm)} \\ 
\\[-1.8ex] & & \textit{OLS} & \textit{robust} \\ 
 & & \textit{} & \textit{linear} \\ 
\\[-1.8ex] & & (1) & (2)\\ 
\hline \\[-1.8ex] 
Species & Chinstrap & 9.566$^{***}$ & 9.911$^{***}$ \\ 
 (Ref: Adelie) & & (0.350) & (0.390) \\ 
  & & \\ 
 & Genotoo & 6.404$^{***}$ & 6.687$^{***}$ \\ 
&  & (1.030) & (1.028) \\ 
 & & & \\ 
Island & Dream &  & $-$0.538 \\ 
(Ref: Biscoe) &  &  & (0.412) \\ 
&  & & \\ 
& Torgersen &  & 0.034 \\ 
 & &  & (0.430) \\ 
&  & & \\ 
\multicolumn{2}{l}{Bill depth (mm)} & 0.313$^{**}$ & 0.320$^{**}$ \\ 
 & & (0.154) & (0.142) \\ 
&  & & \\ 
\multicolumn{2}{l}{Flipper length (mm)} & 0.069$^{***}$ & 0.062$^{***}$ \\ 
 & & (0.023) & (0.023) \\ 
&  & & \\ 
\multicolumn{2}{l}{Body mass (g)} & 0.001$^{**}$ & 0.001$^{**}$ \\ 
 & & (0.0004) & (0.0004) \\ 
&  & & \\ 
Sex & Male & 2.030$^{***}$ & 2.331$^{***}$ \\ 
(Ref: Female) &  & (0.389) & (0.356) \\ 
&  & & \\ 
\multicolumn{2}{l}{ Year} &  & 0.289$^{*}$ \\ 
&  &  & (0.149) \\ 
&  & & \\ 
\multicolumn{2}{l}{ Constant} & 15.017$^{***}$ & $-$563.241$^{*}$ \\ 
&  & (4.374) & (297.257) \\ 
&  & & \\ 
\hline \\[-1.8ex] 
\multicolumn{2}{l}{Observations} & 333 & 333 \\ 
\multicolumn{2}{l}{R$^{2}$} & 0.839 &  \\ 
\multicolumn{2}{l}{Adjusted R$^{2}$} & 0.836 &  \\ 
\multicolumn{2}{l}{Residual Std. Error} & 2.217 (df = 326) & 1.889 (df = 323) \\ 
\multicolumn{2}{l}{F Statistic} & 282.270$^{***}$ (df = 6; 326) &  \\ 
\hline 
\hline \\[-1.8ex] 
\multicolumn{2}{l}{\textit{Note:}}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 
